A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-21 03_Prep_data.Rmd
Save median AUDPC so it can be retrieved in the manuscript
Added an inspection of data on the efficacy of fungicide when fungicide applications are late

@@

>>>>

write.csv(median_AUDPC, here("cache/median_AUDPC_C.csv"), row.names = FALSE)

@@

### Mungbeans age and yield saved
The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
Lets have a look at the age of each trial when each powdery mildew infected it.
We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity.
```{r age_andYield}
dat1 <- slimmer_PM_dat %>%
   mutate(days2PM = first_sign_disease - planting_date)%>%
   arrange(desc(days2PM))%>%
   select(trial_ref, year, location,spray_management, days2PM,grain_yield.t.ha, 
          yield_gain, prop_yield_gain,  AUDPC_m,D_pres,PM_final_severity)
dat1
```
From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
Therefore I will not inspect, `AM1304` (Marys Mount).

We can see that the crops which were likely the most mature, did not show large yield gains, in particular:
   * Hermitage 2019  
   * Premer  
   * Goolhi  
   * Millmerran

Lets look at this in a quick box plot. 
We will only look at trials where powdery mildew set in at flowering which is approximately 60 days after planting.
```{r ageBoxPlot}
dat1 %>%
   filter(days2PM >= 60) %>%
   filter(spray_management != "control" &
             trial_ref != "AM1304" )%>%
   group_by(trial_ref,spray_management)%>%
   ggplot(aes(x= spray_management, y = yield_gain, colour = trial_ref))+
   geom_boxplot()+
   geom_hline(yintercept = 0)
```
We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application.

For completeness lets test this with powdery mildew infection commencing 40 - 60 days after planting, instead of greater than 60.

```{r PM40_2_59_days}
dat1 %>%
   filter(days2PM < 60 &
             days2PM >= 40) %>%
   filter(spray_management != "control")%>%
   group_by(trial_ref,spray_management)%>%
   ggplot(aes(x= spray_management, y = yield_gain, colour = trial_ref))+
   geom_boxplot()+
   geom_hline(yintercept = 0)
```
We can see here all four experiments benefited, on average, from more than one spray.

Lets estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_means` which include some observations of crop maturity.

```{r whatAreTheAges}
dat2 <- PM_MB_means%>%
   mutate(flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
          pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
          late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date))%>%
   select(location, year, flower, pod, late_pod)%>%
   distinct()%>%
   arrange(desc(flower))

index1 <- apply(dat2, 1 , function(X) !all(is.na(X[c("flower", "pod", "late_pod")])))

dat2[index1,]   
as.double(mean(dat2[index1,"flower"], na.rm = TRUE))
as.double(mean(dat2[index1,"pod"], na.rm = TRUE))
as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))
```

We can see that flowering and podding can be variable, and depends on the cumulative degree days <!-- reference here to APSIM model-->. 
however on average flowering starts `r as.double(mean(dat2[index1,"flower"], na.rm = TRUE))` days after sowing, podding starts `r as.double(mean(dat2[index1,"pod"], na.rm = TRUE))`, and late podding `r as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))`

```{r}
#filter(location == "Premer" | location == "Millmerran")%>%
   group_by(trial, trial_ref,location,year)%>%
   summarise(latent = mean(days2PM))%>%
   pull(latent)

sum(temp2 < 60)/length(temp2)

dat2[,c("flower", "pod", "black_pod")]

mean(   
-0.030637255,
-0.058210784)

mean(
-0.076933551,
-0.087826797)
```
